### 2022-02-24 tikz/xlrm.tex
a major reorganization is underway, this is just an intermediate saved point
better figures color schemes and some updates to text

\usepackage{xcolor}
\definecolor{TurquoiseGreen}{HTML}{B8D5B8}
\definecolor{TealBlue}{HTML}{598392}
\definecolor{YellowOrange}{HTML}{FFB140}
\definecolor{RichBlack}{HTML}{011627}

@@

\tikzstyle{uncertainty} = [rectangle, draw, fill=red!30, text=RichBlack, text width=6.5em, text centered]
\tikzstyle{lever} = [rectangle, draw, fill=yellow!20, text=RichBlack, text width=6.5em, text centered]
\tikzstyle{relation} = [rectangle, draw, fill=gray!20, text=RichBlack, text width=6.5em, text centered]
\tikzstyle{metric} = [rectangle, draw, fill=blue!20, text=RichBlack, text width=6.5em, text centered]

\tikzstyle{line} = [draw, very thick, color=RichBlack, ->]
\tikzset{>=latex}

@@

    \node [relation] (relationships) at (0, 0) {System\\Relationships\\(R)};
    \node [uncertainty] (surge) at (-3.5, 2.5) {Storm Surge\\{\footnotesize ($J$ draws from 1 posterior)}};
    \path [line] (surge) to (relationships);
    \node [uncertainty] (slr) at (-3.5, -1) {Sea Level Rise\\{\footnotesize ($J$ Simulations)}};
    \path [line] (slr) to (relationships);
    \node [lever] (elevate) at (0, 2.5) {How high to elevate?};
    \path [line] (elevate) to (relationships);
    \node [metric] (ccost) at (3.5, 1.25) {Construction Costs};
    \path [line] (relationships) to (ccost);
    \node [metric] (fcost) at (3.5, -1.25) {Flood Damages};
    \path [line] (relationships) to (fcost);

    \node[uncertainty] (rcp) at (-4.5, -2.5) {RCP Scenario\\{\footnotesize (4 Scenarios)}};
    \node[uncertainty] (ice) at (-4.5, 0.75) {Ice Sheet Dynamics\\{\footnotesize (3 Models)}};
    \path [line] (rcp) to (slr);
    \path [line] (ice) to (slr);

>>>>

\usepackage{xcolor}
\definecolor{giallo}{HTML}{F0BC42}
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\definecolor{thirds}{HTML}{31467A}
\definecolor{orange}{HTML}{F18101}
\definecolor{deepblue}{HTML}{CA3CFF}

@@

\tikzstyle{uncertainty} = [rectangle, draw, fill=rosso, text=grigio, text width=6.5em, text centered]
\tikzstyle{lever} = [rectangle, draw, fill=giallo, text=nero, text width=6.5em, text centered]
\tikzstyle{relation} = [rectangle, draw, fill=thirds, text=grigio, text width=6.5em, text centered]
\tikzstyle{metric} = [rectangle, draw, fill=orange, text=nero, text width=6.5em, text centered]

\tikzstyle{line} = [draw, very thick, color=nero, ->]
\tikzset{>=latex}

@@

    \node [font=\color{rosso}\selectfont] at (-4.5, 3.5) {\Large Uncertainties};
    \node [relation] (relationships) at (0, -0.5) {Cost and damage models};
    \node [uncertainty] (surge) at (-3.25, 2.5) {Storm surge\\{\footnotesize (draws from 1 posterior)}};
    \path [line] (surge) to (relationships);

    \node [font=\color{thirds}\selectfont] at (0, -1.75) {\Large Relationships};
    \node [uncertainty] (slr) at (-3.5, -1) {Sea level rise\\{\footnotesize (16 PDFs)}};
    \path [line] (slr) to (relationships);

    \node [font=\color{giallo}\selectfont] at (0, 3) {\Large Levers};
    \node [lever] (elevate) at (0, 2) {How high to elevate?};
    \path [line] (elevate) to (relationships);

    \node [font=\color{giallo}\selectfont] at (3.5, 2.25) {\Large Metrics};
    \node [metric] (ccost) at (3.5, 1) {Up-front\\(construction)\\cost};
    \path [line] (relationships) to (ccost);
    \node [metric] (fcost) at (3.5, -1) {Lifetime expected damages};
    \path [line] (relationships) to (fcost);

    \node[uncertainty] (rcp) at (-4.5, -2.5) {RCP scenario\\{\footnotesize (4 Scenarios)}};
    \node[uncertainty] (ice) at (-4.5, 0.75) {Ice sheet dynamics\\{\footnotesize (4 Models)}};
    \path [line] (rcp) to (slr);
    \path [line] (ice) to (slr);
